\documentclass[10pt,a4paper]{article}

\usepackage{fontspec}
\setmainfont{texgyreheros}[
  Extension = .otf,
  UprightFont = *-regular,
  BoldFont = *-bold,
  ItalicFont = *-italic,
  BoldItalicFont = *-bolditalic,
  Scale = 0.95
]
\usepackage[a4paper,top=1.4cm,bottom=1.4cm,left=1.6cm,right=1.6cm]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{needspace}

\definecolor{accent}{HTML}{1F3A5F}
\definecolor{muted}{HTML}{555555}

\hypersetup{colorlinks=true,urlcolor=accent}

\pagestyle{empty}

\titleformat{\section}{\large\bfseries\color{accent}}{}{0pt}{}[\vspace{-6pt}\rule{\linewidth}{0.6pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

\newcommand{\role}[3]{%
  \needspace{6\baselineskip}%
  \textbf{#1} \hfill \textcolor{muted}{#3}\\[-2pt]
  \textit{#2}\par\vspace{2pt}
}

\setlist[itemize]{leftmargin=1.1em,topsep=2pt,itemsep=1pt,parsep=0pt}

\begin{document}

% --- Header ---
\begin{center}
  {\Huge\bfseries\color{accent} Silvio Valerio De Pasquale}\\[4pt]
  {\large Senior Engineering Manager \textemdash{} Cloud, Data \& Platform}\\[6pt]
  \small
  \href{mailto:silvio@depasquale.dev}{silvio@depasquale.dev} \;|\;
  Como, Italy \;|\;
  \href{https://linkedin.com/in/svdepasquale}{linkedin.com/in/svdepasquale} \;|\;
  \href{https://github.com/svdepasquale}{github.com/svdepasquale} \;|\;
  \href{https://silvio.depasquale.dev}{silvio.depasquale.dev}
\end{center}

% --- Summary ---
\section*{Profile}
Engineering leader with 10+ years in cloud and platform engineering, currently managing managers and staff engineers across Cloud, Platform, Operations and Data at Satispay (European fintech, 5M+ users).

Grew the Cloud \& Data organisation from 1 to 10+ engineers with zero turnover over 6 years, scaled the production footprint from 20 to 150+ microservices, and shifted operations from a ticket-based model to platform-as-a-product while holding a 99.95\% SLA.

% --- Experience ---
\section*{Experience}

\role{Senior Cloud Engineering Manager}{Satispay \textbullet{} Milan, Italy (Hybrid)}{Apr 2026 -- Present}
\begin{itemize}
  \item Manager of managers for the Cloud, Platform, Operations and Data Engineering area; line-manage the managers of Platform and Operations and the staff engineers across the group.
  \item Accountable for the technical strategy and people development of 10+ engineers (plus product and senior staff partners) covering cloud infrastructure, internal developer platform, production operations and the data platform.
  \item Driving the next phase of the \textbf{Kubernetes platform} (foundational layer already in production): internal service-to-service traffic management, service mesh adoption and a \textbf{modern APM observability stack}, shaping edge patterns and developer experience.
  \item Maintain a \textbf{99.95\% production SLA} on the payments platform while continuing organisational and architectural change.
  \item Primary technical contact with cloud vendor (TAM engagement, Well-Architected Reviews, roadmap alignment) and owner of multi-account governance, security posture and compliance controls.
\end{itemize}

\role{Cloud Engineering Manager}{Satispay \textbullet{} Milan, Italy}{Mar 2025 -- Apr 2026}
\begin{itemize}
  \item Grew the Cloud \& Data team from 1 to 10+ engineers with \textbf{zero turnover over 6 years} across hot-market hiring conditions; covered infrastructure, data platform and security, reporting to the CTO as primary cloud technical reference.
  \item Introduced career frameworks, hiring and onboarding processes; grew staff engineering and first-line management layers inside the team.
  \item Shaped the platform-engineering roadmap and standards: golden paths, GitHub Actions CI/CD, IaC (Terraform, CloudFormation), multi-account AWS governance.
  \item Shipped an \textbf{internal developer portal} for product-team self-service, with selected operations (e.g.\ alarm provisioning) running as \textbf{fully agentic flows} guarded by \textbf{policy-as-code} in CI; drove a \textbf{30\% reduction in tickets} to the Cloud team within months of rollout.
  \item Led the \textbf{foundational introduction of Kubernetes} to the platform, delivering the first production workload and the GitOps layer in parallel.
\end{itemize}

\role{Associate Cloud Engineering Manager / Cloud Team Lead}{Satispay \textbullet{} Milan, Italy}{May 2022 -- Mar 2025}
\begin{itemize}
  \item Scaled the production platform from 20 to 150+ microservices while maintaining high availability for a payments workload.
  \item Established hiring bar, onboarding, engineering standards and on-call practices for the growing Cloud \& Data team.
  \item Led the infrastructure build-out of Satispay's \textbf{data platform} on AWS building blocks -- SNS event ingestion, Kinesis Firehose pipelines, Redshift as the warehouse, S3 as landing/archival layer -- with \textbf{dbt} on top for modelling and transformation.
  \item Led the \textbf{edge gateway redesign} after DDoS / abusive traffic incidents: edge pattern blocking (WAF), geographic rate limiting on hot paths and per-endpoint isolation, replacing all-or-nothing throttling with surgical mitigation.
\end{itemize}

\role{Senior Cloud Engineer / Cloud Architect}{Satispay \textbullet{} Milan, Italy}{Oct 2020 -- May 2022}
\begin{itemize}
  \item Led the AWS handover from an external consultancy: knowledge transfer, stabilisation and full internal ownership of the platform.
  \item \textbf{Terraformed the entire AWS footprint} by importing existing resources, \textbf{redesigned the VPC networking topology}, and rolled out \textbf{end-to-end CI/CD} where coverage was previously partial.
\end{itemize}

\role{Senior IT Consultant / Cloud Architect / Project Manager}{Reply S.p.A. (Red Reply) \textbullet{} Milan, Italy}{Apr 2019 -- Oct 2020}
\begin{itemize}
  \item Delivered Oracle Cloud migrations for major Italian enterprise clients across telco, insurance, healthcare no-profit and real estate: presales, TCO analysis, project management and delivery.
  \item Acted as customer TAM: SLA management, 24/7 on-call on 100+ node estates, ITIL incident/problem/change processes.
\end{itemize}

\role{IT Consultant / Cloud Architect}{Reply S.p.A. (Red Reply) \textbullet{} Milan, Italy}{Jun 2016 -- Apr 2019}
\begin{itemize}
  \item Delivered Oracle Cloud IaaS/PaaS implementations: hybrid connectivity (IPsec, FastConnect), middleware (WebLogic, Tomcat, nginx) in HA.
  \item Designed cloud networking and monitoring (Zabbix, Nagios, ELK); built internal cloud services and REST APIs.
\end{itemize}

% --- Skills ---
\section*{Selected Skills}
\textbf{Leadership:}\ manager of managers, staff+ engineer coaching, hiring, career frameworks, org design, platform-as-a-product.\\
\textbf{Cloud \& Platform:}\ AWS (Organizations, IAM Identity Center, ECS/Fargate, EC2, RDS, DynamoDB, S3, VPC, Security Hub, Config), Kubernetes, ArgoCD, Helm, Oracle Cloud.\\
\textbf{Networking \& Edge:}\ VPC design, service-to-service traffic management, service mesh adoption, IPsec/VPN, WAF and edge security, IAM, multi-account governance.\\
\textbf{Data:}\ SNS/Kinesis event ingestion, Firehose, Redshift, S3 lakehouse patterns, dbt for modelling and transformation.\\
\textbf{IaC \& Delivery:}\ Terraform, CloudFormation, GitHub Actions, GitOps.\\
\textbf{Observability \& Reliability:}\ Grafana APM stack (Prometheus, Loki, Tempo, Grafana Alloy), CloudWatch, on-call and incident practices.\\
\textbf{AI-augmented management:}\ Claude as single pane for day-to-day engineering-management work --- planning, reviews, ops, knowledge work --- backed by a persistent memory layer that carries context across teams, initiatives and decisions.\\
\textbf{Personal infra:}\ self-hosted k3s + ArgoCD homelab cluster with GitOps and full observability stack (Grafana, Loki, Tempo, Alloy).

% --- Certifications ---
\section*{Certifications}
\begin{itemize}
  \item AWS Certified Developer -- Associate \hfill \textcolor{muted}{Jul 2024 -- Jul 2027}
  \item AWS Certified SysOps Administrator -- Associate \hfill \textcolor{muted}{Feb 2023 -- Feb 2026}
  \item AWS Certified Solutions Architect -- Associate \hfill \textcolor{muted}{Jun 2021 -- Jun 2024}
  \item Certificate of Competence in English (CEFR B2), ICIMS \hfill \textcolor{muted}{Aug 2022 -- Jul 2024}
  \item ITIL v4 Foundation, AXELOS \hfill \textcolor{muted}{Dec 2019}
  \item Oracle Cloud Infrastructure -- Architect \& Operations, Oracle DB 12c, Oracle Linux 6 \hfill \textcolor{muted}{2016 -- 2020}
\end{itemize}

% --- Education ---
\section*{Education}
\role{MSc in Computer Science and Engineering}{Politecnico di Milano \textbullet{} Communication and Society Engineering (English track)}{2009 -- 2016}
\vspace{-2pt}
Grade: 109/110. Thesis: \textit{Analysis of Approximation Techniques for Parallel Computing Applications}. Final master year overlapped with start of consulting role at Reply.

% --- Languages ---
\section*{Languages}
Italian (native) \quad\textbullet\quad English (professional working proficiency)

\vfill
{\scriptsize\color{muted}
\textcopyright{} 2026 Silvio Valerio De Pasquale. Source: \href{https://github.com/svdepasquale/curriculum-vitae}{github.com/svdepasquale/curriculum-vitae}.\\
I authorise the processing of my personal data contained in this CV in accordance with Regulation (EU) 2016/679 (GDPR) and Italian Legislative Decree 196/2003 as amended by D.Lgs. 101/2018.
}

\end{document}
